A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit result 1

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  \minn{} display a large diversity in their stellar haloes. In Paper~1, we explored the \mstar{}-dependence of the stellar haloes in massive 
    galaxies, and concluded that the general trends are consistent with the 
    predictions of the two-phase formation scenario. In this paper, we now investigate the relation between galaxy profiles, their stellar halos, and dark matter halo mass. Here we use \mtot{} as proxy for the ``total'' \mstar{}
    of massive galaxies and we use \minn{} as a rough proxy for the mass of the 
    \textit{in situ} component.  We remind the reader that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and estimate 
    \mtot{} and \minn{} using elliptical apertures following the average fluxed-weighted isophotal shape.

    % We said this already...
    %Also,given the narrow \mstar
    %{} and redshift range, we ignore \mstar{} growth 
    %and structural evolution.

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on halo mass at fixed stellar mass. To ask this question, however, we must first define which stellar mass exactly is being fixed in the comparison. We will show results both when we fix \mtot{} as well as when we fix \minn{}. We also ensure that all comparisons are performed with a fixed underlying redshift distribution by mathcing samples in redshift in addition to stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, and Fig~\ref{fig:match} for details).

@@

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies living in low mass dark matter haloes to those living in high mass dark matter haloes at fixed \mtot{} 
    (left panel) and at fixed \minn{} (right panel). This Figure shows the main result of this paper, namely that \textbf{the \mden{} profiles of 
    massive central galaxies show a clear dependence on dark matter halo mass at both fixed \mtot{} and 
    \minn{}.}

    We perform several statistical tests to demonstrate that the differences we see in the median 
    \mden{} profiles are significant. We also conduct a variety of tests that verify the robustness of these results with respect choices regarding \mtot{} bins, our $\lambda$ cut, the redshift range, and the choice of apertures used for the metric masses. Please see Appendix~\ref{app:robust} for further details.

@@

        \item For the \mtot{} matched sample, although there is a clear and robust difference between the two median \mden{} profiles, the overall difference is subtle is mainly only apparent on $R>50$ kpc scales. This may explain why previous attempts to detect this signal using shallower images were not successful. 
        \item At fixed \mtot{}, central galaxies in high mass dark matter haloes display shallower \mden{} profiles compared to those living in low mass dark matter haloes (they have a flatter inner \mden{} profiles and more significant outer stellar haloes. 
        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross each 
            other at ${\sim} 15$-20 kpc, roughly also the scale of the effective radius $R_{\mathrm{e}}$.      
        \item Finally, the differences between the two sets of profiles becomes more prominent at higher \mtot{}. This can be seen further dividing the sample into two \mtot{} bins (see Fig~\ref{fig:prof_2} and discussion in 
            Appendix~\ref{app:robust}) and when we discuss the relation between \mtot{} and 
            \minn{} (see Fig~\ref{fig:scaling_relation}). This trend has potentially interesting implications \alexie{can we explain in one phrase?} that will be investigated in follow-up work. 
    \end{itemize}

\alexie{lets chat about the following two paragraphs}
    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

@@

@@

%% ------------------------------------------------------------------------------------ %% 
\section{E. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}

>>>>

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
    \minn{} display a large diversity in their stellar haloes. 
    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
    galaxies, and concluded that the general trends are consistent with the predictions 
    of the two-phase formation scenario. 
    In this work, we now investigate the relation between the \mden{} profiles of 
    massive galaxies, their stellar halos, and dark matter halo mass. 
    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
    component.  
    We remind the reader that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
    estimate \mtot{} and \minn{} using elliptical apertures following the average 
    fluxed-weighted isophotal shape.

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass. 
    To ask this question, however, we must first define which stellar mass exactly is 
    being fixed in the comparison. 
    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
    \minn{}. 
    We also ensure that all comparisons are performed with fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

@@

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
    fixed \minn{} (right panel). 
    This figure shows the main result of this paper, namely that 
    \textbf{the \mden{} profiles of massive central galaxies show a clear dependence on 
    dark matter halo mass at both fixed \mtot{} and \minn{}.}

    We perform several statistical tests to demonstrate that the differences we see in 
    the median \mden{} profiles are significant. 
    We also conduct a variety of tests that verify the robustness of these results with
    respect to the choices of \mtot{} bins, $\lambda$ cut, the redshift range, and the 
    choice of apertures used for the metric masses. 
    Please see Appendix~\ref{app:robust} for further details.

@@

        \item For the \mtot{} matched sample, although there is a clear and robust 
            difference between the two median \mden{} profiles, the overall difference 
            is subtle is mainly only apparent on $R>50$ kpc scales. 
            The logarithmic scale of \mden{} on the Y-axis is partially responsible 
            for the subtle differences we see here.  
            In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same
            comparison using the curve--of--growth of \mstar{} and the fraction of 
            \mtot{} enclosed in elliptical apertures with different radius. 
            Both of the illustrate the same results from slightly different angles.

        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
            display shallower \mden{} profiles compared to those living in low mass 
            dark matter haloes (they have a flatter inner \mden{} profiles and 
            more significant outer stellar haloes.

        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.

        \item Finally, the differences between the two sets of profiles becomes 
            more prominent at higher \mtot{}. 
            This can be seen further dividing the sample into two \mtot{} bins 
            (see Fig~\ref{fig:prof_2} and discussion in Appendix~\ref{app:robust}) 
            and when we discuss the relation between \mtot{} and 
            \minn{} (see Fig~\ref{fig:scaling_relation}). 
            This trend has potentially interesting implications

            \alexie{can we explain in one phrase?} that will be investigated in follow-up work.

%This may explain why previous attempts to detect this signal using 
            %shallower images were not successful. 
\alexie{lets chat about the following two paragraphs}
    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the \textit{in situ} mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo.

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/redbcg_prof_m100D}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.
        }
    \label{fig:cog}
\end{figure}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\section{E. Stellar Mass Curve-of-Growth for Massive Central Galaxies} 
	\label{app:cog}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{F. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}
